%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\usepackage{enumitem}
\renewenvironment{entrylist}{%
  \begin{itemize}[leftmargin=1in]%[leftmargin=*,align=left,itemindent=-\dimexpr\labelwidth+\labelindent+\labelsep\relax]
}{%
  \end{itemize}
}
\renewcommand{\bfseries}{\headingfont\color{headercolor}}
\renewcommand{\entry}[4]{%
  \item[#1]
    \textbf{#2}%
    \hfill%
    {\footnotesize\addfontfeature{Color=lightgray} #3}\\%
    #4\vspace{\parsep}%
  }

\begin{document}
\header{Alexander}{Papiez}
       {%Research Chemist
       	}
       {}


% In the aside, each new line forces a line break  
\begin{aside}
 \vspace{-0.5cm}
  \section{Contact}
    30 Ullswater Road
    Kettering
    Northamptonshire
    NN16 8UD
    ~
    \href{mailto:alex.papiez@gmail.com}{alex.papiez@gmail.com}
    ~
    Tel:07584357494
    ~
  \section{Key Skills}
   \begin{itemize}
   \item 14 Years laboratory experience
   \item Mentoring and Teaching experience
   \item Proficient in use of SAGE 50 and CIM50
   \item Experienced user of Microsoft Office packages
   \item Able to work well independently and in a group
   \item Ability to work to a deadline/ \\ under pressure
   \item Programming \\ languages: \\ C#, Python (proficient) Rust (learning)
   \rule[0.125cm]{0.6\textwidth}{0.4pt}\\
   \item Full U.K. Driving\\ Licence and own car
   \rule[0.125cm]{0.6\textwidth}{0.4pt}
   \end{itemize}

\end{aside}
\vspace{-0.6cm}


\section{Profile}
Following the completion of my PhD in 2017, I moved into the chemical manufacturing industry. Starting as a development chemist, reponsible for product development and quality control
testing, I quickly moved to the role of Chief Chemist, responsible for management of the lab, before moving to the role of Technical Director.
In these various roles, I have developed experience in many domains - from business development and crisis management, to team leadership and product stewardship.
During my time in the industry I have nurtured a keen interest in sustainable business practices. I have been proud to be part of a small team which has achieved 
significant recognition for such practices; both in the holistic sense (with such accreditations as B-Corp) and related to specific products (e.g the Cruelty Free International accreditation). 
As a former academic I have a keen eye for detail and am always interested in learning new things. 
This passion has allowed me to work across a number of domains with proficiency. 
I am very self motivated and can accomplish anything I set my mind to. I am at my happiest when my work contributes to the success of my colleagues and the overall wellbeing of my team. 

%\section{Profile}
%My attention and eye for detail have allowed me to be successful in my research career. As a self sufficient individual I have shown initiative in promptly solving problems which have arisen. In early 2016 I was invited to the International Congress on Marine Corrosion and Fouling in Toulon, France; where I presented aspects of my work to attendees. During the course of my studies I have consistently developed my ability to communicate ideas in a clear and concise manner while maintaining an engaging connection with the audience. I believe this is key to building rapports and successful working relationships. 
\section{Employment}

\begin{entrylist}
    \entry
    {03/2021-Present}
    {Technical Director}
    {Ideal Manufacturing Ltd}
    {\emph{As Technical Director, I am ultimately responsible for all technical functions of the business. As we are a very small team, the range of functions this encompasses is large. 
    I ensure that all regulations which apply to the business (HSWA, DSEAR, COSHH e.t.c.) are followed and that all staff are cognizant of their duties arising from same. 
    I also directly support and manage commercial aspects of the business. This involves everything from setting and promulgating product prices to holding commercial discussions with prospective suppliers and clients. 
    I administer the company IT network, managing and provisioning software and hardware to ensure the team has the requisite capacity, as well as liaising with vendors to ensure our requirements are met. 
    }\vspace{0.2cm}\hrule}

    \entry
    {09/2018-03/2021}
    {Chief Chemist}
    {Ideal Manufacturing Ltd}
    {\emph{In addition to existing practical duties, I became responsible for managing the growing lab team to ensure delivery of goals according to company strategy. In this capacity I provided mentorship to new members of the technical team. During this time I also became the appointed Dangerous Goods Safety Advisor for the company.}\vspace{0.2cm}\hrule}
    \entry
    {01/2017-09/2018}
    {Development Chemist}
    {Ideal Manufacturing Ltd}
    {\emph{Responsible for the development of new products, including formulation, Safety Data Sheet preparation and the preparation and delivery of information to customers. In this capacity I learned how to formulate a wide range of household and industrial cleaning products. In this capacity I was also responsible for quality control testing manufactured products.}\vspace{0.2cm}\hrule}
    \entry
    {09/2013-05/2016}
    {Lab Demonstrator}
    {Northumbria University}
    {\emph{Worked to support the safe operation of lab-practical classes for undergraduate students. My knowledge in the field and previous experience with the course content meant I was able to act as an effective mentor and role model to students, helping to support the learning experience provided by the lecturer.}\vspace{0.2cm}\hrule}
    \entry
    {02/2015 - 05/2015}
    {GCE A-Level Tutor (Chemistry)}
    {Newcastle Upon Tyne}
    {\emph{I provided one-to-one tutoring support to a student preparing to sit their chemistry A-Level exams. I developed a lesson plan for each session covering a specific topic to ensure that student was given the best opportunity to understand the content and succeed in the exams.}\vspace{0.2cm}\hrule}
    \entry
    {06/2013 - 09/2013}
    {Production operative / Packer}
    {Quorn Foods, Stokesley}
    {\emph{During the summer I worked as part of a team on the  Quorn production line. Duties included packing and  palletizing the product, quality control, cleaning and some work in clean production areas.}\vspace{0.2cm}\hrule}
  
 \end{entrylist}
\section{Education}

\begin{entrylist}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\entry
	{09/2013-01/2017}
	{PhD in Physical Polymer Chemistry}
	{Northumbria University}
	{\emph{Supervisors:} Dr. Justin Perry and Dr. Leslie Dix\\
		\vspace{-0.4cm}\rule[0.325cm]{0.8\textwidth}{0.4pt}\\
		\emph{Funded by:} \phantom{lll}AkzoNobel/International Paint\\
		\vspace{-0.4cm}\rule[0.325cm]{0.8\textwidth}{0.4pt}\\
		\emph{Thesis title:} \phantom{.}Investigating the Rate of Release of Ions Across Polymer  \phantom{Thesis titlelil:} Phases\\
		\vspace{-0.4cm}\rule[0.325cm]{0.8\textwidth}{0.4pt}\\
		\emph{Summary:}\phantom{.....}In order to develop competitive products in a sustainable\\ \phantom{Summary:.....}manner, anti-fouling paint manufacturers must consider the\\ \phantom{Summary:.....}kinetics of biocide release. By studying the diffusion rate of \phantom{Summary:.....}biocides in relation to material properties, insights useful for \phantom{Summary:.....}the rational design of anti-fouling technologies may be found.
		\\
		\vspace{-0.4cm}\rule[0.3cm]{0.8\textwidth}{0.4pt}\\
		\emph{Publications:}\phantom{.}{\small\textbf{Papiez}, A.P. Perry, J.J.B Ferguson, J. Wright, A.C.\\\phantom{Publications:...}\emph{Diffusion of Biocides in Polymeric Matrices: A Tool for Rational\\ \phantom{Publications:...}Coating Design}, Poster presented at the International Congress \\ \phantom{Publications:...}on Marine Corrosion and Fouling, Toulon France, 2016\\
			\phantom{Publications:.............................................}\vspace{-0.2cm}{\large*} \\ 
			\phantom{Publications:..}
			\textbf{Papiez}, A.P. Perry, J.J.B. Downs, R.A.\emph{Design and Implementation\\ \phantom{Publications:...}of a 3D Printed Microwave Flow Cell}, Poster presented at the R.S.C.\\ \phantom{Publications:...}Organic division meeting, Bradford, U.K. 2015\\	
			\hrule}}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\entry
	{09/2009 - 06/2013}
	{MChem Applied Chemistry}
	{Northumbria University}
	{\emph{Classification:} 1st with honours\\
		\vspace{-0.4cm}\rule[0.3cm]{0.8\textwidth}{0.4pt}\\ 
		\emph{Awards:} \phantom{lalelul}Best Post-graduate final-year project, 2013\\
		\vspace{-0.4cm}\rule[0.3cm]{0.8\textwidth}{0.4pt}\\
		\emph{4th Year} \phantom{lalelul}Synthesis and Characterization of Amino Functionalized\\
		\emph{Project:}\phantom{lalelu...}Methacrylate Polymers\\
		\vspace{-0.4cm}\rule[0.3cm]{0.8\textwidth}{0.4pt}\\
		\emph{3rd Year} \phantom{lalelul}Predicting Mass Spectra Using Density \\
		\emph{Project:}\phantom{lalelu...}Functional Theory Calculations \\
		\hrule
	}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\entry
	{09/2007-07/2009}
	{GCE A-Levels}
	{Stokesley Sixth Form College}
	{\emph{A2:}\phantom{LaLeLuLiL..}Physics, Chemistry, Mathematics\\
		\vspace{-0.4cm}\rule[0.3cm]{0.8\textwidth}{0.2pt}\\
		\emph{AS:}\phantom{LaLeLulll....}Physics, Chemistry, Mathematics, French
		\hrule
	}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\entry
	{09/2002-07/2007}
	{GCSEs}
	{Stokesley Comprehensive School}
	{10 at grade A*-C including Maths, English and Science\\ \hrule}

\end{entrylist}

\section{Interests}
I am a proficient programmer and enjoy the creative thinking involved in solving technical problems; in conjunction with amateur DIY, I enjoy producing software and hardware to tackle real world problems. 
\\

I am an avid reader - my favourite genre is historical non-fiction as I enjoy learning about the past and the lessons it holds for today's world. This spurs my interest in politics and current affairs, which I enjoy debating in great detail. \\

I love the operas of Gilbert and Sullivan, my favourites being The Mikado and Iolanthe. I am fascinated by the intricate combination of language and musical theatre which they employ to make clever satirical comments.\\





\section{References}
References available on request.
%\begin{multicols}{2}
%\justify
%\emph{Dr.Justin Perry},\\
%\textbf{Enterprise Fellow}\\
%Health and Life Sciences\\
%Northumbria University,\\
%Ellison Building,\\
%Ellison Place,\\
%Newcastle Upon Tyne,\\
%NE1 8ST,\\
%Phone: 0191 227 3554,\\
%Email:justin.perry@northumbria.ac.uk\\

%\emph{Dr. Leslie Dix},\\
%\textbf{Senior Lecturer},\\
%Health and Life Sciences\\
%Northumbria University,\\
%Ellison Building,\\
%Ellison Place,\\
%Newcastle Upon Tyne,\\
%NE1 8ST,\\
%Phone: 0191 227 3510,\\
%Email: les.dix@northumbria.ac.uk
%\end{multicols}
\end{document}
